\chapter{Introduction}
\label{introduction}

Over the past years, autonomy has played a vital role in the development of automobiles. The vehicles have moved from being a pure mechanical wonder to a software and hardware combination. The developments are fuelled by advancement in low-cost sensor technology and government regulations to improve the safety of road transportation. At the same time, there is an increasing demand for fully autonomous vehicles with its potential in improving road safety and business services.

The past decade has seen a significant improvement in the development of technology for the autonomous vehicles bringing the science fiction of robots driving people a step closer. This technology has the potential for substantial societal impacts by reducing the fatalities in car accidents to changing the ecosystem of transportation. World Health Organization reports that every year there are more than 1.25 million deaths and between 20-50 million people suffer non-fatal injuries worldwide because of road accidents \cite{whoaccidents}. The accidents are because of many reasons such as road conditions, vehicle condition, driver alertness etc. The advancements in self-driving technology have a potential to reduce the risks by keeping track of road without distractions reducing human error, and also react quickly in emergency situations.

Increase in the urban population in many cities around the world is leading to increased traffic congestion, this has effects on health and productivity of the people \cite{citycongestion}. Increase in congestion is a result of growth in car ownership, to combat congestion cities like Singapore are banning new car ownership \cite{singaporebanscars}. Autonomous cars have the potential to shape the future of transportation by reducing car ownership, thus contributing to the reduction in congestion of cities. The report \cite{morgenstanleyreport} from Morgen Stanley analyses the further impacts of the autonomous cars on industry and society. 


\section{Motivation}

Autonomous vehicles are at the forefront of the research in automotive industry, to bring the technology closer to everyday use there needs to be further research. The new research required is mainly in the areas of urban driving involving a large number of traffic participants and complex road conditions. Though robots can act deterministically, humans and environment are not deterministic, to make autonomous vehicles safe the research should be focused at understanding these interactions.

To work on full-scale autonomous vehicles are expensive, time taking, and safety critical to test in emergency scenarios for understanding these interactions. Though simulators provide easy ways to evaluate the situations, issues caused by physical aspect of the perception and vehicle control are missing in simulators. Research into autonomous vehicles is also an expensive endeavour with high costs on platforms, operational constraints and involves large teams. Model cars (1:10 scaled versions of cars) can break this barrier to bring the technology closer to a large number of researchers in the world thus, being the enabler for further innovation. These Modelcars share the aspects of fully autonomous vehicles concerning expected behaviour and conventional mobile robots regarding sensor and computational resources sharing similar challenges of autonomous cars. 

The challenges in autonomous vehicles can be subdivided into sensing/perception, navigation and control. The challenge under consideration in this thesis is the navigation/planning problem of driving the ego vehicle (vehicle in consideration for planning) to the destination with available resources. The problem of planning is unique as the module is responsible for understanding the behaviour of the surrounding objects and adjust the ego vehicle's behaviour accordingly following specific rules and react appropriately. Though motion planning for autonomous vehicles is a widely researched topic in structured environments, these methods cannot be applied to the model cars due to constraints in computational power, sensor measurements and vehicle control. The methods proposed in classic mobile robots research either consider dynamic obstacles as pseudo-dynamic (momentarily static) or moving in a straight line not considering the road properties. There is a need for a planner to address these issues. 

\section{Problem Statement}

The underlying problem of trajectory planning can be considered as a general robot path planning problem where the robot has to find a path avoiding obstacles, following constraints and moving on it. It can be formulated as an optimal control problem to determine set of states $x(t)$ or controls $u(t)$ for a dynamic system (ego vehicle) over a time (planning horizon) to minimise a performance index in a dynamic environment $r(t)$. The performance index could be one or multiple parameters such as distance to the goal, following various constraints such as no collision, maintaining the speed limit, comfort etc.


% There exist well-known methods within the domain of the robot/autonomous vehicle path planning that can be adapted to achieve trajectory planning for a model car. Model cars are limited to the available resources such as computational power, perception data, accuracy in measurements etc. Thus, these approaches need to be tailor-made to suit the model car platforms.

%The challenge is to create trajectory planner considering limitations of these small platforms and achieving the behaviour of an autonomous car.

\section{Thesis Statement}

This thesis advocates that effective trajectory planning for modelcars in a structured environment similar to fully autonomous vehicles can be achieved at a low computational cost by combining prediction and approximation techniques in trajectory creation and evaluation.

\section{Thesis Contributions}

The main contribution of this thesis is the introduction of a trajectory generation framework and algorithms for smaller model car platforms. The hierarchical framework employed divides the problem into four layers of planning named route planner, behavioural layer, trajectory planner and control node. The focus is the development of trajectory creation algorithm using samples of acceleration profiles and lateral shifts, an algorithm to pre-assign costs to samples such that planner evaluates the paths based on pre-costs and converges faster to the solution. The final contribution is collision detection algorithm that works in two steps for detecting collision with static obstacles and three steps for dynamic obstacles. 

\section{Thesis Structure}


The thesis is broadly organised as follows. The initial chapters present relevant research in this field, followed by a chapter outlining the target hardware and software platform setup, and approach to motion planning. Implementation overview, evaluation and conclusion follow the approach.

Firstly, Chapter \ref{related_work} introduces the research direction in autonomous vehicles, followed by different planning approaches in on-road driving. Next, an overview of different trajectory representation and evaluation techniques is presented.

Chapter \ref{vehicle_info} provides a basic overview of the software and hardware architecture of the target platform.

Chapter \ref{planning_algo} provides a detailed illustration of the motion planning algorithms developed for this thesis followed by evaluation techniques to validate the trajectories by checking for collision.

Chapter \ref{implementation} provides a basic overview of the implementation of the proposed planning algorithm by describing the structure of different modules implemented and message flow across them.

Chapter \ref{evaluation} details on the different experiments performed to validate the planner followed by general criteria-based evaluation of the proposed planner.

Finally. Chapter \ref{conclusion} concludes regarding the work done in this thesis, discusses regarding possible improvements and further research options.
